manuscript - APP

### 2018-07-03 R/manuscript_app.Rmd
test anovas with factor
We were using linear predictor instead of categorical

df_exp2a %>% 
  filter(restk2 == "Fast-moving-distractors") %>% 
  ez::ezANOVA(dv = accuracy,
        wid = as.factor(subject),
        within = as.factor(type), 
        detailed = T) %>% 
  apa::anova_apa()
```

>>>>

df_exp2a %>% 
  filter(restk2 == "Fast-moving-distractors") %>% 
  ez::ezANOVA(dv = accuracy,
        wid = as.factor(subject),
        within = as.factor(type), 
        detailed = T) %>% 
  apa::anova_apa()

df_exp2a %>% 
  filter(restk2 == "Slow-moving-distractors") %>% 
  mutate(type2 = as.character(type)) %>% 
  ez::ezANOVA(dv = accuracy,
        wid = subject,
        within = type2, 
        detailed = T) %>% 
  apa::anova_apa(sph_corr = "none")

df_exp2a %>% 
  filter(restk2 == "Fast-moving-distractors") %>% 
  mutate(type2 = as.character(type)) %>% 
  ez::ezANOVA(dv = accuracy,
        wid = as.factor(subject),
        within = as.factor(type2), 
        detailed = T) %>% 
  apa::anova_apa(sph_corr = "none")
```
